Results

### 2024-04-05 Sections/Results.qmd
toc update

---
title: Results
author: "Thomas Gorman"
toc: true
toc-location: right
# number-sections: true
# number-depth: 5
strip-comments: true
cold-tools: true
echo: false
format: 
  # html:
  #   column: 
  #     - screen-inset-right
  hugo-md:
    echo: false
    html-math-method: mathjax
    output-file: full-results-hugo.md
  # gfm:
  #   echo: true
  #   output-file: e1-gfm.md
#toc: true
# toc-title: Contents
# toc-depth: 4
# toc-expand: 1
# execute:
#   echo: false
---

>>>>

---
title: Results
author: "Thomas Gorman"
toc: true
toc-location: right
# number-sections: true
# number-depth: 5
# strip-comments: true
# cold-tools: true
echo: false
#format: 
  # html:
  #   column: 
  #     - screen-inset-right
  # hugo-md:
  #   echo: false
  #   html-math-method: mathjax
  #   output-file: full-results-hugo.md
  # gfm:
  #   echo: true
  #   output-file: e1-gfm.md
#toc: true
# toc-title: Contents
# toc-depth: 4
# toc-expand: 1
# execute:
#   echo: false
---
